### 2018-12-09 Sections/errors_in_quantum_networks.tex
Few figs, NOON state loss

When implementing protocols employing post-selection upon detecting all photons, the protocol will be non-deterministic, where loss dictates the protocol's success probability. Specifically, with $n$ photons, each with efficiency $\eta$, the net post-selection success probability\index{Post-selection success probability} of the entire device is,
\begin{align}
	P=\eta^n.
\end{align}
This implies an exponential number of trials\index{Trials},
\begin{align}
	N=\left(\frac{1}{\eta}\right)^n,
\end{align}
is required in post-selected protocols. Clearly this exponential scaling is of concern, requiring demanding efficiencies in future large-scale implementations.

@@

Formally, let $\mathcal{E}^\mathrm{loss}_\eta$ be the loss channel with efficiency $\eta$. The channel acting on an initially pure single-photon state, $\ket{1}$, can be modelled as a beamsplitter with transmissivity $\eta$ acting on the state, where the reflected mode is traced out, shown in Fig.\ref{fig:loss_model}. This yields the quantum process,
\begin{align}
\mathcal{E}^\mathrm{loss}_\eta(\hat\rho) = \mathrm{tr}_B[\hat{U}_\mathrm{BS}(\hat\rho_A\otimes\ket{0}_B\bra{0}_B)\hat{U}_\mathrm{BS}^\dag],
\end{align}
where $\hat{U}_\mathrm{BS}$ is the beamsplitter operation.

@@

In the special case of linear optics circuits, loss channels have the elegant property that, provided the loss rate is uniform across all modes, they can be commuted through the circuit to the front or back \cite{???}\index{Loss!Commutation}. Specifically,
\begin{align}
(\mathcal{E}_{\eta}^\mathrm{loss})^{\otimes m} \circ \mathcal{E}_U = \mathcal{E}_U \circ (\mathcal{E}_{\eta}^\mathrm{loss})^{\otimes m},
\end{align}
where $\mathcal{E}_U$ is a unitary linear optics process, implementing a photon-number-preserving map of the form of Eq.~(\ref{eq:LO_unitary_map}). This simplifies the treatment of distinct system inefficiencies (such as source, network and detector inefficiencies) by allowing us to commute them to the beginning or end of the circuit and combine them together into a single net efficiency. In many scenarios, this allows the different system inefficiencies to be dealt with via post-selection.

@@

Similarly, NOON states (Sec.~\ref{sec:NOON}) undergo complete wave-function collapse if just a single photon is lost to the environment, and because there are $N$ photons in total, the probability of wave-function collapse grows exponentially with photon-number.

>>>>

When implementing protocols employing post-selection upon detecting all photons, the protocol will be non-deterministic, where loss dictates the protocol's success probability. Specifically, with $n$ photons, each with efficiency $\eta$, the net post-selection success probability\index{Post-selection success probability} of the entire device is,
\begin{align}
	P=\eta^n.
\end{align}
This implies an exponential number of trials\index{Trials},
\begin{align}
	N = \frac{1}{P} = \frac{1}{\eta^n},
\end{align}
is required in post-selected protocols. Clearly this exponential scaling is of concern, requiring demanding efficiencies in future large-scale implementations.

@@

Formally, let $\mathcal{E}^\mathrm{loss}_\eta$ be the loss channel with efficiency $\eta$. The channel acting on an initially pure single-photon state, $\ket{1}$, can be modelled as a beamsplitter with transmissivity $\eta$ acting on the state, where the reflected mode is traced out, shown in Fig.~\ref{fig:loss_model}. This yields the quantum process,
\begin{align}
\mathcal{E}^\mathrm{loss}_\eta(\hat\rho) = \mathrm{tr}_B[\hat{U}_\mathrm{BS}(\hat\rho_A\otimes\ket{0}_B\bra{0}_B)\hat{U}_\mathrm{BS}^\dag],
\end{align}
where $\hat{U}_\mathrm{BS}$ is the beamsplitter operation.

@@

In the special case of linear optics circuits, loss channels have the elegant property that, provided the loss rate is uniform across all modes, they can be commuted through the circuit to the front or back \cite{???}\index{Loss!Commutation}. Specifically,
\begin{align}
(\mathcal{E}_{\eta}^\mathrm{loss})^{\otimes m} \circ \mathcal{E}_U = \mathcal{E}_U \circ (\mathcal{E}_{\eta}^\mathrm{loss})^{\otimes m},
\end{align}
where $\mathcal{E}_U$ is a unitary linear optics process, implementing a photon-number-preserving map of the form of Eq.~(\ref{eq:LO_unitary_map}). This is represented by the circuit diagram shown in Fig.~\ref{fig:loss_LO_commutation}. This simplifies the treatment of distinct system inefficiencies (such as source, network and detector inefficiencies) by allowing us to commute them to the beginning or end of the circuit and combine them together into a single net efficiency. In many scenarios, this allows the different system inefficiencies to be dealt with via post-selection.

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{loss_LO_commutation}
	\captionspacefig \caption{Commutation of a uniform loss channel (i.e identical efficiency on each mode), $\mathcal{E}^\mathrm{loss}$, through a passive linear optics network, $\hat{U}$.} \label{fig:loss_LO_commutation} \index{Loss!Commutation}
\end{figure}

@@

Similarly, NOON states (Sec.~\ref{sec:NOON}) undergo complete wave-function collapse if just a single photon is lost to the environment. This is because any single photon reveals complete information about the location of the remaining \mbox{$N-1$} photons. Therefore, a NOON state subject to loss of a single photon decoheres to the mixture,
\begin{align}
\hat\rho = \frac{1}{2}(\ket{N-1,0}\bra{N-1,0} + \ket{0,N-1}\bra{0,N-1}),
\end{align}
which contains no entanglement.

Because there are $N$ photons in total, the probability of wave-function collapse grows exponentially with photon-number. Specifically, the probability of completely collapsing and losing all entanglement is,
\begin{align}
	P=1-\eta^N,
\end{align}
as shown in Fig.~\ref{fig:NOON_loss}.

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{NOON_loss}
	\caption{Probability of an $N$-photon NOON state completely collapsing and losing all entanglement, under a loss channel with efficiency $\eta$.}\label{fig:NOON_loss}
\end{figure}
